From Precipitation to Prediction: Integrating ConvLSTM Models for Comprehensive River Runoff Forecasting

### 2024-03-18 paper/paper.tex
update newest

\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[borderline west={3pt}{0pt}{shadecolor}, breakable, enhanced, interior hidden, sharp corners, frame hidden, boxrule=0pt]}{\end{tcolorbox}}\fi

@@

\includegraphics{images/paste-5.png}

\includegraphics{images/paste-6.png}

\hypertarget{acknowledgments}{%
\section{Acknowledgments}\label{acknowledgments}}

>>>>

\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[borderline west={3pt}{0pt}{shadecolor}, enhanced, boxrule=0pt, interior hidden, breakable, sharp corners, frame hidden]}{\end{tcolorbox}}\fi

@@

\includegraphics{images/paste-7.png}

\hypertarget{acknowledgments}{%
\section[Acknowledgments]{\texorpdfstring{\protect\includegraphics{images/paste-8.png}Acknowledgments}{Acknowledgments}}\label{acknowledgments}}
